Resilience and Home-Space for WSTS \thanks{This work was partly done while the authors were supported by the Agence Nationale de la Recherche grant BraVAS (ANR-17-CE40-0028).}

### 2023-10-30 VMCAI-revised-version/final.tex
effectivity

In the case of $\pred$-basis-effective (upward) compatible WSTS, {\sc Resilience} is undecidable when $\Safe = \mathop{\downarrow} \Safe$.  This stems from the fact
{\sc Resilience} when $\Safe= \{ q_f({\bf 0}) \}$ for some control-state $q_f$ is equivalent to
deciding structural %termination of reset-VASS, 
			existential halting of reset-VASS, 
which is undecidable.

Indeed, the structural existential halting problem consists in deciding if 
a system %terminates
have a \alain{un ou tous les run ?}terminating (i.e. finite) run
 from every initial state.

@@

{\sc Structural existential halting} is undecidable which leads to the following proposition.

>>>>

%In the case of $\pred$-basis-effective (upward) compatible WSTS, {\sc Resilience} is undecidable when $\Safe = \mathop{\downarrow} \Safe$.  This stems from the fact
%{\sc Resilience} when $\Safe= \{ q_f({\bf 0}) \}$ for some control-state $q_f$ is equivalent to
%deciding structural %termination of reset-VASS, 
%			existential halting of reset-VASS, 
%which is undecidable.

We now prove that {\sc Resilience} is undecidable for reset-VASS, hence it will be also undecidable for (upward) compatible WSTS when $\Safe = \mathop{\downarrow} \Safe$.
%
%Indeed, the structural existential halting problem consists in deciding if 
%a system %terminates
%have a terminating (i.e. finite) run
% from every initial state.

@@

{\sc Structural existential halting} is undecidable since termination is undecidable for deterministic counter machines.

%			which leads to the following proposition.
